An efficient composition of bidirectional programs by tupling and lazy updates

### 2020-02-18 paper/4.xpg.tex
update initialization because of renaming

\smallvspace
    $\tab s \Leftarrow s_0; v \Leftarrow v_0; (ks, kv, s, v) \Leftarrow \cpg{bx}{\lambda \_.s}{id}{s}{v};\\
        \tab \qtab (s; v)$
\smallvspace

In general, the beginning of a continuation should be an identity function. However, to be able to use the function application to get the result of $\cpginline{bx_1 \circ bx_2}$, the accumulative function on the source $s$ needs to be initiated as $\lambda \_.s$. This constant function helps to retain the discarded things in the source.

@@

\smallvspace
    $\tab s \Leftarrow s_0; v \Leftarrow v_0; (ks, kv, lks, lkv, s, v) \Leftarrow \kpg{bx}{\lambda \_.s}{id}{id}{id}{s}{v};\\
        \tab \qtab (lks \ s; lkv \ v)$
\smallvspace

>>>>

\smallvspace
    $\tab (ks, kv, s, v) \Leftarrow \cpg{bx}{\lambda \_.s_0}{id}{s_0}{v_0};\\
        \tab \qtab (s; v)$
\smallvspace

In general, the beginning of a continuation should be an identity function. However, to be able to use the function application to get the result of $\cpginline{bx_1 \circ bx_2}$, the accumulative function on the source needs to be initiated as the constant function from that source. This constant function helps to retain the discarded things in the source.

@@

\smallvspace
    $\tab (ks, kv, lks, lkv, s, v) \Leftarrow \kpg{bx}{\lambda \_.s_0}{id}{id}{id}{s_0}{v_0};\\
        \tab \qtab (lks \ s; lkv \ v)$
\smallvspace

### 2020-02-18 paper/5.experiments.tex
update initialization because of renaming

We have 
% conducted 
selected seven test cases (Table~\ref{tab:test-cases}) to 
represent
% assess 
non-trivial cases of practical significance.
The test cases use
% These $bx$s are 
left associative compositions because we focus on this kind of inefficiency in this paper.
% Although the number of cases is small, 
%% they are not trivial and can be completely used in practice. 
% they represent non-trivial cases of practical significance.
In the last two columns, $s_r$ and $v_r$ are the updated source and view, respectively. They are produced by applying $put$ and $get$ to the original source $s_0$ and view $v_0$. That is, $s_r = \putbx{bx}{s_0}{v_0}$ and $v_r = \getbx{bx}{s_0}$, where $bx$ is the program indicated in the second column of the table. 
% are only interested in this kind of programs in the paper. 
% Please note that the results
Results $s_r$ and $v_r$ are independent of the associativity 
% style 
of the composition.

\begin{table}[hbt!]
    \centering
    \caption{Composition test cases (number of compositions = $n$)}
    \label{tab:test-cases}
    \begin{tabular*}{\textwidth}{|l @{\extracolsep{\fill}}|l|l|c|c|c|c|}
        \hline
        \multirow{2}{*}{No} & \multicolumn{1}{c|}{\multirow{2}{*}{Name}} & \multicolumn{1}{c|}{\multirow{2}{*}{Type}} & \multicolumn{2}{c|}{Input} & \multicolumn{2}{c|}{Output} \\ \cline{4-7} 
        & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{$s_0$} & \multicolumn{1}{c|}{$v_0$} & \multicolumn{1}{c|}{$s_r$} & \multicolumn{1}{c|}{$v_r$} \\ \hline
        1 & lcomp-phead-ldata & straight line & $\underbrace{[[\ldots[1]\ldots]]}_{\text{n+1 times}}$ & 100 & $\underbrace{[[\ldots[100]\ldots]]}_{\text{n+1 times}}$ & 1 \\ \hline
        2 & lcomp-ptail & straight line & [1,$\ldots$,n+1] & [1,$\ldots$,10] & $s_0 \ @ \ v_0$ & [\ ] \\ \hline
        3 & lcomp-ptail-ldata & straight line & $\underbrace{[L,\ldots,L]}_{\text{n+1 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{10 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n+11 times}}$ & [\ ] \\ \hline
        4 & lcomp-bsnoc & straight line & [1,$\ldots$,n-1] & [1,$\ldots$,n-1] & [1,$\ldots$,n-1] & [1,$\ldots$,n-1] \\ \hline
        5 & lcomp-bsnoc-ldata & straight line & $\underbrace{[L,\ldots,L]}_{\text{n-1 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n-1 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n-1 times}}$ & $\underbrace{[L,\ldots,L]]}_{\text{n-1 times}}$ \\ \hline
        6 & breverse & recursion & [1,$\ldots$,n] & [1,$\ldots$,n] & [n,$\ldots$,1] & [n,$\ldots$,1] \\ \hline
        7 & breverse-ldata & recursion & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ \\ \hline
    \end{tabular*}
\end{table}

>>>>

We have 
% conducted 
selected seven test cases (Table~\ref{tab:test-cases}) to 
represent
% assess 
non-trivial cases of practical significance.
The test cases use
% These $bx$s are 
left associative compositions because we focus on this kind of inefficiency in this paper.
% Although the number of cases is small, 
%% they are not trivial and can be completely used in practice. 
% they represent non-trivial cases of practical significance.
In the last two columns, $s$ and $v$ are the updated source and view, respectively. They are produced by applying $put$ and $get$ to the original source $s_0$ and view $v_0$. That is, $s = \putbx{bx}{s_0}{v_0}$ and $v = \getbx{bx}{s_0}$, where $bx$ is the program indicated in the second column of the table. 
% are only interested in this kind of programs in the paper. 
% Please note that the results
Results $s$ and $v$ are independent of the associativity 
% style 
of the composition.

\begin{table}[hbt!]
    \centering
    \caption{Composition test cases (number of compositions = $n$)}
    \label{tab:test-cases}
    \begin{tabular*}{\textwidth}{|l @{\extracolsep{\fill}}|l|l|c|c|c|c|}
        \hline
        \multirow{2}{*}{No} & \multicolumn{1}{c|}{\multirow{2}{*}{Name}} & \multicolumn{1}{c|}{\multirow{2}{*}{Type}} & \multicolumn{2}{c|}{Input} & \multicolumn{2}{c|}{Output} \\ \cline{4-7} 
        & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{$s_0$} & \multicolumn{1}{c|}{$v_0$} & \multicolumn{1}{c|}{$s$} & \multicolumn{1}{c|}{$v$} \\ \hline
        1 & lcomp-phead-ldata & straight line & $\underbrace{[[\ldots[1]\ldots]]}_{\text{n+1 times}}$ & 100 & $\underbrace{[[\ldots[100]\ldots]]}_{\text{n+1 times}}$ & 1 \\ \hline
        2 & lcomp-ptail & straight line & [1,$\ldots$,n+1] & [1,$\ldots$,10] & $s_0 \ @ \ v_0$ & [\ ] \\ \hline
        3 & lcomp-ptail-ldata & straight line & $\underbrace{[L,\ldots,L]}_{\text{n+1 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{10 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n+11 times}}$ & [\ ] \\ \hline
        4 & lcomp-bsnoc & straight line & [1,$\ldots$,n-1] & [1,$\ldots$,n-1] & [1,$\ldots$,n-1] & [1,$\ldots$,n-1] \\ \hline
        5 & lcomp-bsnoc-ldata & straight line & $\underbrace{[L,\ldots,L]}_{\text{n-1 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n-1 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n-1 times}}$ & $\underbrace{[L,\ldots,L]]}_{\text{n-1 times}}$ \\ \hline
        6 & breverse & recursion & [1,$\ldots$,n] & [1,$\ldots$,n] & [n,$\ldots$,1] & [n,$\ldots$,1] \\ \hline
        7 & breverse-ldata & recursion & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ \\ \hline
    \end{tabular*}
\end{table}
